\thetitle

### 2021-03-03 writing/rational-experiment.tex
touch ups in section 5

In detail, the answer to $Q_1$ demands a comparison of the success of the Natural
blame and Natural exception trails for all debugging scenarios.  The
first step is to construct each mutant's scenario lattice and identify their
debugging scenarios.  The experiment then extends the trails that start
from those roots according to the Natural-blame programmer.  If no scenarios can
be added to the trail, the experiment checks whether the last scenario
of the trail type-checks or not. If it does, the
Natural-blame trail is successful; otherwise it is failing. 
Figure~\ref{fig:process} summarizes this experimental process for
one mode of the rational programmer and connects it with the mutations from
section~\ref{sec:mutate}.
The experiment repeats the process for the same roots with the other mode, Natural
exceptions.
After completing, the experiment
reports the success/failure results of the trails to determine the proportion of
scenarios where Natural blame is more useful than Natural exceptions.  Question
$Q_1$ has a positive answer if a root exists where the above is true because it
is evidence that there is at least one interesting scenario that the rational
programmer manages to debug with blame information.  The process is analogous
for $Q_2$ and $Q_3$, using the respective modes of the rational programmer.

>>>>

In detail, the answer to $Q_1$ demands a comparison of the success of the Natural
blame and Natural exception trails for all debugging scenarios.  The
first step is to construct each mutant's scenario lattice and identify their
debugging scenarios.  The experiment then extends the trails that start
from those roots according to the Natural-blame programmer.  If no scenarios can
be added to the trail, the experiment checks whether the last scenario
of the trail type-checks or not. If it does, the
Natural-blame trail is successful; otherwise it is failing. 
Figure~\ref{fig:process} summarizes this experimental process for
one mode of the rational programmer and connects it with the mutations from
section~\ref{sec:mutate}.
The experiment repeats the process for the same roots with the other mode, Natural
exceptions.
After completing, the experiment
reports the success/failure results of the trails to determine the proportion of
scenarios where Natural blame is more useful than Natural exceptions.  Question
$Q_1$ has a positive answer if a root exists where the above is true because it
is evidence that there is at least one interesting scenario that the rational
programmer manages to debug because of blame information.  The process is analogous
for $Q_2$ and $Q_3$, using the respective modes of the rational programmer.

### 2021-03-03 writing/rational-natural.tex
touch ups in section 5

While a successful Natural blame trail indicates that it 
pays off to heed blame assignments during debugging the trail's root, it does not answer whether
blame is a critical piece of the rational programmer's process.  For instance,
typing the top of a failed run time type check's stack trace, dubbed the
location of the exception, might be as useful as typing the blamed one.

>>>>

While a successful Natural blame trail indicates that it 
pays off to heed blame assignments while debugging the trail's root, it does not answer whether
blame is a critical piece of the rational programmer's process.  For instance,
typing the top of a failed run-time type check's stack trace, dubbed the
location of the exception, might be as useful as typing the blamed one.

### 2021-03-03 writing/rational.tex
touch ups in section 5

Each mode receives different kinds of information and thus may construct
different paths in the lattice. As discussed in~\ref{sec:challenges},
evaluating blame relies on comparing modes of the rational programmer
within the same semantics and across different semantics.

>>>>

Each mode receives different kinds of information and thus may construct
different paths in the lattice. As discussed in section~\ref{sec:challenges},
evaluating blame relies on comparing modes of the rational programmer
within the same semantics and across different semantics.
